Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-22 Draft/Draft20181218.Rmd

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

* 70% of import value from China is coming from 8 products 
* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
* %70 is from commodities and mineral fuels for import from Russia
* Only commodities constitute 43% of total import of Russia
* Vehicles other than railway is the top product imported from Germany
* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles

#### PIE GRAFIGI DEGISTIRECEGIZ DİYE SHINY DEN IMAGE LARI ALMADIM HENUZ

@@

@@

## References

>>>>

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    #toc_float:
     # collapsed: true
      #smooth_scroll: true
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

@@

* 70% of import value from China is coming from 8 products while 50% is from electrical machinery, equipments and machinery, mechanical appliances

![Import from China](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\ChinaImport.png)

* Mineral fuels, mineral oils and products of their distillation constitute %21 of import from Russia, while the bigggest product group is classified as "Other""

![Import from Russia](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\RussiaImport.png)

* Vehicles other than railway is the top product imported from Germany and mechanical and electronical machinery and equipments are followed it.

![Import from Germany](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\GermanyImport.png)

@@

### Analysis of the Import Unit Prices and Export Unit Prices

In order to understand the products which Turkey is both exporting and importing but importing with more value addition, we calculated unit prices on each product for both import and export and we followed finding the ratio of Import Unit Price / Export Unit Price and groping them in bins of 10.

```{r}

unit_price_import <- import_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
  mutate(Unit_Price = Values/Quantity)
unit_price_export <- export_jTableMELTED %>% select(Country,Product_Label, X__2 ,Product_Label, Product_Label, Unit, Quantity, year, Values) %>% 
  mutate(Unit_Price = Values/Quantity)

unit_price_import <- unit_price_import %>% mutate(type="Import") 
unit_price_export <- unit_price_export %>% mutate(type="Export")

joint_table <- unit_price_export %>% select(Country,Product_Label,year,Export_Unit_Price=Unit_Price) %>% 
  full_join(unit_price_import, by =c("Country","Product_Label","year")) %>% select(Country,Product_Label,year,Export_Unit_Price,Import_Unit_Price=Unit_Price) %>%
  mutate(Ratio=Import_Unit_Price/Export_Unit_Price)
melted_data <- joint_table %>% melt(id=c("Country","Product_Label","year","Ratio")) %>% rename("type"=variable) %>% 
  filter(value  >0 & Ratio >0 & Ratio !=Inf ) #& Ratio <=1000 & value <=10000)

melted_data <- melted_data %>% mutate(Bins=0)
melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" ) ) %>%  
  select(Country,Product_Label, year, Ratio, Bins) 
melted_data <- distinct(melted_data)

 # &  Bins!="21-30"
```

```{r, fig.align="center", fig.height=7, fig.width=10}

ggplot(melted_data, aes(Bins)) + 
  geom_bar(aes(fill=year), width = 0.5) +

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 20 times",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```

As seen in the graph;

* France, Germany, UK and US are the strongest countries in terms of buying products from Turkey, adding value to these products and selling back to Turkey.

In order to examine the details, we builded ***[Shiny](https://groupfour.shinyapps.io/tradeOrgProUnitP/)*** app.

* xxx

* xxx

* xxx

@@

## References
[TradeMap](https://trademap.org/Index.aspx)
[TCMB](http://tcmb.gov.tr)
[TUIK](http://www.tuik.gov.tr/)
[Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
[R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
[R-statistics blog](https://www.r-statistics.com/tag/transpose/)
